### 2023-09-23 sections/languages.tex
Update languages.tex

\cvskill
{Languages} 
{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), Italian}

\cvskill
{} 
{(elemental reading skills), French (elemental reading skills)} \\

\cvskill
{Programming \&} 
{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}

\cvskill
{Software} 
{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}} \\

>>>>

\cvskill
{Languages} 
{\textcolor{black}{Spanish (native speaker), English (fluent), Portuguese (advanced reading skills), Italian}}

\cvskill
{} 
{\textcolor{black}{(elemental reading skills), French (elemental reading skills)}} \\

\cvskill
{Programming \&} 
{\textcolor{black}{R, Python, Stata, {\scshape spss/pspp}, Gephi, {\scshape ucinet}, NetDraw, Tosmana, Fuzzy-Sets, ArcGIS, {\scshape atlas}.ti,}}

\cvskill
{Software} 
{\textcolor{black}{EndNote, Zotero, {\scshape HPoP}, {\LaTeX}, Bib{\TeX}, JabRef, MS Office, WordPress, Moodle, {\scshape html}, {\scshape css}, {\scshape xhtml}}} \\
